\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}
    \usepackage{fontawesome} 
    \usepackage{setspace} 
    \usepackage[pdfnewwindow=true]{hyperref}
    \hypersetup{pdfnewwindow}
    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}
    

%==== Profile ====%
\vspace*{-5pt}
\begin{center}
	{\Huge \scshape {Kyle Balisnomo}}\\
	Edmonton, AB, Canada $\cdot$ kylebalisnomo@gmail.com $\cdot$ 780-860-0914 \\
    \href[pdfnewwindow=true]{https://linkedin.com/in/kyle-balisnomo/}{\faLinkedinSquare\ kyle-balisnomo} $\cdot$ \href[pdfnewwindow=true]{https://github.com/kbalisnomo}{\faGithub\ kbalisnomo} \\
\end{center}

%==== Skills ====%
\header{Technical Skills}
\vspace{1mm}

\begin{tabular}{ l l } 
	Programming Languages:    & Kotlin, Java, Python, C, C++, JavaScript, Bash, HTML/CSS                      \\
	Frameworks and Databases: & Dropwizard, Kotest, Pytest PostgreSQL, React, Django, Express                 \\
	AWS:                      & IAM, Lambda, SQS, SNS, S3, API Gateway, RDS,                                  \\
                              & DynamoDB, EC2, SES, CloudFormation, Secrets Manager                           \\
    Tools:                    & Git, Postman, Datadog, Docker, Kubernetes, Terraform,                         \\
                              & Swagger, PagerDuty, Atlassian (Confluence, Jira, Bitbucket)                   \\
\end{tabular}

\vspace{2mm}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{Intermediate Software Developer} \hfill Edmonton, AB, Canada (Remote)\\
\textit{INVIDI Technologies} \hfill June 2022 - Present \\
Engineered high-performance, scalable, and fault-tolerant applications using Kotlin, Kubernetes, and AWS for the INVIDI Conexus™ platform.
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Developed and maintained a critical component handling 100,000+ ad inventory requests daily.
    \item Recognized as the recipient of the prestigious 2023 INVIDI Best Talent Award for outstanding contributions to the team.
    \item Implemented RESTful APIs with OAuth 2.0 authentication, securing data exchange between system components.
	\item Introduced automated email notifications for customers regarding pending advertisement slots, leading to a 15\% boost in client impressions.
    \item Managed cloud infrastructure across 10+ environments using Terraform and Datadog.
    \item Contributed to a 24-hour on-call rotation, ensuring a 99.9\% system uptime and minimizing revenue loss.
    \item Mentored and supported new team members, sharing technical expertise and industry insights to accelerate their onboarding process.
\end{itemize}
\vspace{1mm}

\textbf{Software Developer Intern} \hfill Edmonton, AB, Canada (Remote)\\
\textit{INVIDI Technologies} \hfill May 2020 - September 2021\\
Collaborated within a scrum team of 6 to develop Kotlin microservices for the INVIDI Edge™ platform, enabling television distributors and providers to seamlessly deliver targeted advertising to their audience.
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Developed a component responsible for contract management, ensuring precise allocation of ad insertion rights within designated timeframes.
	\item Enhanced code coverage from 60\% to 95\% in existing projects through the implementation of unit and integration tests.
	\item Extended Datadog dashboards and monitors, resulting in a 32\% improvement in incident detection accuracy.
\end{itemize}

\vspace{2mm}

%==== Projects ====%
\header{Projects}
\vspace{1mm}

{\textbf{INVIDI Symphonia}} {\sl Google Gemini, React, Express, Python} \\
A generative music platform, winner of the INVIDI 2024 Hackathon.
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Generated chords and melodies via Google Gemini API.
    \item Translated text data to midi files using Python.
    \item Utilized Material UI for our React frontend.
\end{itemize}
\vspace{1mm}

{\textbf{ISSSRewards}} {\sl React, Django} \hfill \href[pdfnewwindow=true]{https:\\isssrewards.com}{\faLink\ isssrewards.com}\\
A rewards-based web application for The Interdepartmental Science Students' Society at the University of Alberta with 30,000+ members.
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Developed a React frontend and a fully specified REST backend built with Django and PostgreSQL.
	\item You can view a video demo of the project \href[pdfnewwindow=true]{https://youtu.be/DWQUfd3L6-4?si=qhcAEgHnzHFfS7ZZ}{here. \faYoutubePlay}
\end{itemize}
\vspace{1mm}

%==== Education ====%
\header{Education}
\vspace{1mm}

\textbf{University of Alberta}\hfill Edmonton, AB, Canada\\
Bachelor of Science with Specialization in Computing Science \hfill May 2022\\

\end{document}